%-------------------------
% Resume in Latex
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}

\geometry{left=0.85cm, top=0.75cm, right=0.85cm, bottom=0.75cm}
\pagestyle{empty}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands

\newcommand{\resumeExp}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{\textcolor{blue}{#1}} $\cdot$ \small{\textbf{#2}} & {\footnotesize{#3}} {\footnotesize{(#4)}}
    \end{tabular*}
    \vspace{-7mm}
}

\newcommand{\education}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-1.2mm}\\
        \hspace{-4mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-5mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} | \textcolor{blue}{\footnotesize{#2}} | \textcolor{blue}{\footnotesize{#3}} | \emph{\footnotesize{#4}} &  \\
    \end{tabular*}
    \vspace{-8.1mm}
}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=-2.5mm]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-1.5mm}}

\renewcommand{\arraystretch}{1}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}

%-------------------------------------------

\newcommand{\name}{Prathamesh Mali}
\newcommand{\designation}{Senior Frontend Engineer}
\newcommand{\phone}{9892634021}
\newcommand{\emaila}{mali.prathamesh82@gmail.com}
\newcommand{\github}{pratham82}
\newcommand{\linkedin}{prathameshmali}

\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{\name}}
\end{center}
\begin{center}
    \textbf{\designation\ (5+ Years)} $\cdot$ \small{Mumbai, India} \\[0.5mm]
    \small{Frontend Architecture $\cdot$ AI-Assisted Development $\cdot$ Design Systems $\cdot$ Performance Optimization $\cdot$ React Native} \\[0.5mm]
    \color{blue}\small{
    \href{https://pratham82.in}{\faGlobe \hspace{0.2mm} portfolio} |
    \href{https://github.com/\github}{\faGithub \hspace{0.2mm} pratham82} |
    \href{https://www.linkedin.com/in/\linkedin/}{\faLinkedinSquare \hspace{0.2mm} prathameshmali} |
    \href{mailto:\emaila}{\faSend \hspace{0.2mm} \emaila} |
    \faPhone \hspace{0.2mm} +91\phone
    }
\end{center}
\vspace{-3mm}

%-----------SUMMARY-----------------
\section{Summary}
\vspace{1mm}
\small{Senior Frontend Engineer with 5+ years of experience building large-scale web and mobile applications using React.js, Next.js, TypeScript, and React Native. Experienced in frontend architecture, design systems, micro-frontend patterns, and cross-functional collaboration. Currently leading checkout modernization at lululemon while leveraging AI-native engineering workflows to drive productivity.}
\vspace{-2mm}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeExp
{\href{https://www.publicissapient.com/}{Publicis Sapient}}
{Senior Frontend Engineer}
{\textbf{July 2025 – Present}}
{Mumbai}
\resumeItemListStart
\item[$\cdot$] \textbf{lululemon}: Lead a frontend pod within lululemon's checkout platform, driving technical discussions, code reviews, and delivery execution while owning the promotions and discounts domain end-to-end.
\item[$\cdot$] Driving checkout modernization for \href{https://shop.lululemon.com/}{\textcolor{blue}{lululemon.com}}, migrating a legacy JavaScript codebase to Next.js and TypeScript within a micro-frontend architecture (GraphQL, Apollo, Zustand).
\item[$\cdot$] Leveraged AI-assisted development workflows using GitHub Copilot, Claude Code, and agentic tooling to improve developer productivity and accelerate feature delivery.
\item[$\cdot$] \textbf{ADCB Banking}: Contributed to cross-platform digital banking solutions (React Native Expo, XState, Tamagui); built a phonebook onboarding component and a generic approval workflow reused across multiple banking modules.
\resumeItemListEnd

\vspace{2mm}
\resumeExp
{\href{https://www.blitzelectric.id/}{Blitz Electric}}
{Senior Software Engineer (Frontend)}
{\textbf{June 2024 – June 2025}}
{Remote}
\resumeItemListStart
\item[$\cdot$] \textbf{Mobile Seller Platform:} Launched offline sales system with QRIS/cash transactions, geo-tagged returns, and photo verification, driving \textbf{30\%} higher daily sales and \textbf{80\%} fewer deposit disputes across \textbf{100+} stores.
\item[$\cdot$] \textbf{Shipping Fee Engine:} Replaced manual pricing with a real-time calculator (distance, weight, service type), improving order volume by \textbf{20\%} and streamlining partner onboarding.
\item[$\cdot$] \textbf{Design System:} Built a reusable React component library (npm) to standardize UI across multiple teams.
\item[$\cdot$] \textbf{Order Tracking:} Built a partner-facing tracking system (Google Maps API) for Blibli and Lazada, reducing support queries.
\resumeItemListEnd

\vspace{2mm}
\resumeExp
{\href{https://www.mosaicwellness.in/}{Mosaic Wellness}}
{SDE 1}
{\textbf{June 2022 – April 2024}}
{Mumbai}
\resumeItemListStart
\item[$\cdot$] Led development and migration of a consultation booking experience from WebView to React Native, resulting in a \textbf{40\% increase} in appointment bookings and a \textbf{10\% reduction} in funnel drop-offs.
\item[$\cdot$] Built doctor consultation and appointment scheduling systems including an Instant Appointment System (Web) and a chat-based booking flow in the mobile app (React Native).
\item[$\cdot$] Revamped the Track Order page with real-time in-page communications, contributing to a \textbf{5\% decrease} in customer support queries.
\item[$\cdot$] \textbf{Products}: \href{https://manmatters.com/}{\textcolor{blue}{manmatters.com}}, \href{https://bebodywise.com/}{\textcolor{blue}{bebodywise.com}}, \href{https://ourlittlejoys.com/}{\textcolor{blue}{ourlittlejoys.com}}
\resumeItemListEnd

\vspace{2mm}
\resumeExp
{\href{https://www.edstem.com/}{Edstem Technologies}}
{Software Developer}
{\textbf{July 2021 – April 2022}}
{Remote}
\resumeItemListStart
\item[$\cdot$] Built student-facing quiz module and admin dashboard for Lead IAS (Angular Ionic); created a React compliance dashboard for Woodside with Jest unit tests.
\resumeItemListEnd

\vspace{2mm}
\resumeExp
{\href{https://www.edulab.in/}{Edulab}}
{Software Engineer}
{\textbf{February 2021 – June 2021}}
{Mumbai}
\resumeItemListStart
\item[$\cdot$] Built end-to-end LMS features for SDBMI students (MEAN stack) and a Node.js certificate generation tool with pdfmake.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-3mm}

%-----------PROJECTS-----------------
\vspace{-3mm}
\section{Projects}
\resumeSubHeadingListStart
\vspace{1mm}
\resumeProject
{Portfolio}
{\href{https://pratham82.vercel.app/home}{Website}}
{\href{https://github.com/Pratham82/portfolio-v5}{Code}}
{Next.js, TypeScript, Tailwind, GraphQL, Sanity.io, MDX}
\resumeItemListStart
\vspace{2mm}
\item[$\cdot$] Built a personal portfolio and CMS-driven blogging platform using Next.js, GraphQL, Sanity.io and MDX, supporting content publishing, project showcasing, SEO optimization and dynamic content management.
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-3mm}

%-----------SKILLS-----------------
\vspace{-1.2mm}
\section{Technical Skills}

\small{\begin{tabular*}{\textwidth}[t]{p{0.17\textwidth} p{0.79\textwidth}}
\textbf{Frontend}        & Next.js, React.js, TypeScript, React Native, Redux, Zustand, Tailwind CSS, Storybook \\
\textbf{Backend \& APIs} & GraphQL, Apollo Client/Server, Node.js, Express.js, REST APIs \\
\textbf{Testing}         & Jest, React Testing Library \\
\textbf{DevOps \& Tools} & Docker, GitHub Actions, Jenkins, Vercel, Git, Jira \\
\textbf{AI Tools}        & GitHub Copilot, Claude Code, Cursor, Ollama, MCP Integrations \\
\end{tabular*}}

%-----------EDUCATION-----------------
\section{Education}

\education
{Master of Computer Science (Grade: 9.29)}
{Mumbai University}
{\textbf{2019 – 2021}}
{}

\vspace{4mm}

\education
{Bachelor of Computer Science}
{Mumbai University}
{\textbf{2016 – 2019}}
{}

\end{document}
